### 2013-11-13 inst/doc/README.Rmd
updated documentation

```{r}
f <- system.file("examples", "trees.xml", package="RNeXML")
tr <- nexml_read(f, "phylo")
plot(tr[[1]])
```

@@

```{r eval=FALSE} 
ex2 <- nexml_read("treebase1.xml", "nexml")
metadata(ex2)
```

Add metadata to a NeXML tree:

```{r eval=FALSE}
nexml_write(bird.orders, "birds.xml", 
            author="Carl Boettiger <cboettig@ropensci.org>", 
            title = "example NeXML file for bird orders", 
            description = "Example phylogeny taken from the ape documentation showing the major bird orders", 
            in_publication = "doi:10.1010/fakedoi.1234",
            add_itis = TRUE)
```

-->

>>>>

```{r}
library(RNeXML)
f <- system.file("examples", "trees.xml", package="RNeXML")
nexml <- nexml_read(f)
tr <- get_tree(nexml) # or: as(nexml, "phylo")
plot(tr)
```

@@

```{r } 
get_taxa(nexml)
get_metadata(nexml) 
```

--------------------------------------------

Add basic additional metadata:

```{r}
  nexml_write(bird.orders, file="meta_example.xml",
              title = "My test title",
              description = "A description of my test",
              creator = "Carl Boettiger <cboettig@gmail.com>",
              publisher = "unpublished data",
              pubdate = "2012-04-01")

```

### Advanced annotation

We can also add arbitrary metadata to a NeXML tree by define `meta` objects:

```{r}
modified <- new("meta",
                 property = "prism:modificationDate",
                 content = "2013-10-04")
```

Advanced use requires specifying the namespace used.  Metadata follows the RDFa conventions.  Here we indicate the modification date using the prism vocabulary. This namespace is included by default, as it is used for some of the basic metadata shown in the previous example.  We can see from this list:

```{r}
RNeXML:::nexml_namespaces
```

This next block defines a resource (link), described by the `rel` attribute as a homepage, a term in the `foaf` vocabulalry.  Becuase `foaf` is not a default namespace, we will have to provide its URL in the full definition below.

```{r}
website <- new("meta", 
               href = "http://carlboettiger.info", 
               rel = "foaf:homepage")
```

Here we create a history node using the `skos` namespace.  We can also add id values to any metadata element to make the element easier to reference externally:

```{r }
  history <- new("meta", 
      property = "skos:historyNote", 
      content = "Mapped from the bird.orders data in the ape package using RNeXML",
      id = "meta123")
```

Once we have created the `meta` elements, we can pass them to our `nexml_write` function, along with definitions of the namespaces.

```{r}
  nexml_write(bird.orders, 
              file = "example.xml", 
              additional_metadata = list(history, modified, website), 
              additional_namespaces = c(skos = "http://www.w3.org/2004/02/skos/core#",
                                        prism = "http://prismstandard.org/namespaces/1.2/basic/",
                                        foaf = "http://xmlns.com/foaf/0.1/"))

```
